An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-06-03 tex/paper.tex
New plots.
- Removing the ARIMA for number of strategies
- Rerunning the plot for the full tournament
More restructuring.

With a growing collection of 122 strategies, the library is a also a
platform for an original tournament that, in itself, is of interest to the
game theoretic community.

@@

You can see an overview of the structure of the source code in
Figure~\ref{fig:overview}. This shows the parallel collection of strategies and
their tests. Furthermore the underlying engine for the library is a class for
tournaments which lives in the \texttt{tournament.py} module. This class is
responsible for coordinating the play of generated matches. This generation of
matches is the responsibility of a match generator class which is designed in
such a way as to be easily modifiable to create new types of matches. This is
described fuller in a tutorial in the documentation which shows how to easily
create a tournament where players only play each other with probability 0.5.
This will be discussed further in the reuse section of this paper.

@@

Add more here: point to previous discussion about new strategies, new
tournaments, tests etc\dots

>>>>

With a growing collection of 135 strategies, the library is a also a
platform for an original tournament that, in itself, is of interest to the
game theoretic community.

@@

You can see an overview of the structure of the source code in
Figure~\ref{fig:overview}. This shows the parallel collection of strategies and
their tests. Furthermore the underlying engine for the library is a class for
tournaments which lives in the \texttt{tournament.py} module. This class is
responsible for coordinating the play of generated matches (from the
\texttt{match.py} module). This generation of matches is the responsibility of a
match generator class (in the \texttt{match\_generator.py} module) which is
designed in such a way as to be easily modifiable to create new types of
tournaments. This is described fuller in a tutorial in the documentation which
shows how to easily create a tournament where players only play each other with
probability 0.5.  This will be discussed further in the reuse section of this
paper.

@@
